Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
comment
check

We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
We care more about lazy strategies because recently, \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that these strategies are not very ideal. 
\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy
	\\ --- \\ Explained, not sure if it suffice. -KC}

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -Jeremy
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC}

>>>>

We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
We care more about lazy strategies because recently, \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that these strategies are not very ideal. 
\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy
  \\ --- \\ Explained, not sure if it suffice. -KC
  \\ --- \\
  That's good that you explained why lazy instead of eager.
  (Also, you should add that we are interested in lazy because
  that's what Grift does.)\\
  But you haven't explained why we are interested in both D and UD. -JS
}

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is to vague. -JS
        }
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -Jeremy
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
        It's better because it matches the postfix syntax we are using for
        casts. Currently line 2 of applyCast for D is difficult to read,
        compare it with line 4 of applyCast for UD. -JS
        }
